Diagnostic Plots

### 2024-08-15 plots/diagnostic_plots.qmd
Moved diagnostics plots to plots folder

---
title: "Diagnostic Plots"
subtitle: "Self-talk interventions and sport/motor performance: An updated systematic review and Bayesian meta-analysis"
author: "Hannah Corcoran, James Steele"
format:
  pdf:
    documentclass: report
    toc: false
    number-sections: false
    highlight-style: github
    fig-width: 10
    fig-height: 10
---
# Main Model

>>>>

---
title: "Diagnostic Plots"
subtitle: "Cumulative evidence synthesis and consideration of 'research waste' using Bayesian methods: An example updating a previous meta-analysis of self-talk interventions for sport/motor performance"
author: "Hannah Corcoran, James Steele"
format:
  pdf:
    documentclass: report
    toc: false
    number-sections: false
    highlight-style: github
    fig-width: 10
    fig-height: 10
---
```{r,message=FALSE,warning=FALSE,echo=FALSE}
targets::tar_config_set(store = here::here('_targets'))

# Main Model
